Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment

### 2024-07-30 JASA-template.tex
Paragraph.

>>>>

\added{%
Another topic of interest pertinent to medical diagnosis is missing data.
It has been shown that using bounded probability is particularly suitable
for dealing with instances where data cannot be assumed missing at random
\citep{decoomanzaffalon2004}.
Incorporating robustness against missing data could lead to an interesting
extension of the model in this paper.%
}
